On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-02 Manuscript/reply.tex
Comment on Drawbacks in Discussion

>>>>

We also added this comment in the Discussion section:

We discussed some
drawbacks of block bootstrap in the introduction, which could motivate a similar
simulation study for alternatives to block bootstrap, such 
as AR-Sieve bootstrap, \citep{kreiss1992bootstrap} which 
\citet{buhlmann2002bootstraps} finds to be the best for linear time series.
